Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-11-12 numerical-amr.tex
Updating the shear criterion to match the current pending PR.  The old method written for Kritsuk et al 2006 refined on vorticity + shear, not shear alone.

\item{\em Shear.} As described in \citet{Kritsuk06}, turbulence
  calculations can be successfully modeled with AMR if the shear is
  used as a refinement parameter; in particular, refinement occurs
  when the finite difference version of the following inequality
  holds:

\begin{equation}
\sum_i \sum_j \left( \frac{\partial v_i}{\partial x_j} \right)^2 -  \sum_i \left( \frac{\partial v_i}{\partial x_i} \right)^2
> \epsilon_s \frac{c_s^2}{\Delta x^2},
\end{equation}
where $\epsilon_s$ is a dimensionless parameter. The current
implementation assumes that $c_s$ is a constant and that $\Delta x$ in
the above expression is evaluated with the cell size on the level
being tested.

>>>>

\item{\em Shear.} Originally used in \citet{Kritsuk06} and later 
  modified into a more general form, turbulence calculations and
  Kelvin-Helmholtz instabilities can be successfully modeled with AMR if 
  the shear is used as a refinement parameter; in particular, refinement 
  occurs when the finite difference version of the following inequality
  holds:

\begin{equation}
\left| \sum_{i \ne j} \left( \frac{\partial v_i}{\partial x_j} + \frac{\partial v_j}{\partial x_i} \right) \right|
> \epsilon_s \frac{c_s}{\Delta x},
\end{equation}
where $\epsilon_s$ is a dimensionless parameter.
